
%\documentclass[conference]{IEEEtran}
\documentclass[10pt,conference]{IEEEtran}

\pagestyle{plain}

\usepackage[english,american]{babel}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage[colorlinks, linkcolor=red, anchorcolor=green, citecolor=blue]{hyperref}
\usepackage{cite}
\usepackage{balance}
\usepackage{color}
\usepackage[square,sort,comma,numbers]{natbib}
\usepackage{url}
\usepackage{diagbox}
\usepackage{enumerate}
\usepackage{setspace}
\let\labelindent\relax
\usepackage{enumitem}
\usepackage{indentfirst}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{listings}
\usepackage{etoolbox}
\usepackage{setspace}
\usepackage{amsfonts}

\hyphenation{op-tical net-works semi-conduc-tor}
%\renewcommand{\baselinestretch}{0.985}
%\renewcommand{\captionfont}{\linespread{1.5}\normalsize}

%\renewcommand{\thesection}{\arabic{section}}
%\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}
%\renewcommand{\thesubsubsection}{\thesubsection.\arabic{subsubsection}}

%\makeatletter
%\def\@seccntformat#1{\@ifundefined{#1@cntformat}%
%   {\csname the#1\endcsname\quad}%       default
%   {\csname #1@cntformat\endcsname}}%    enable individual control
%\newcommand\section@cntformat{}
%\makeatother

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%\usepackage{setspace}
%\usepackage{epsfig,graphics,subfigure,psfrag,amsmath,amssymb}
\newcommand\FIXME[1]{\textcolor{red}{FIX:}\textcolor{red}{#1}}
\newcommand\FIXED[1]{\textcolor{blue}{FIXED: }\textcolor{blue}{#1}}

\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

%\def\@IEEEsectpunct{.\ \,}
%\def\paragraph{\@startsection{paragraph}{4}{\z@}{1.5ex plus 1.5ex minus 0.5ex}%
%{0ex}{\normalfont\normalsize\sffamily\bfseries}}


\newcommand{\circled}[2][]{\tikz[baseline=(char.base)]
    {\node[shape = circle, draw, inner sep = 1pt]
    (char) {\phantom{\ifblank{#1}{#2}{#1}}};%
    \node at (char.center) {\makebox[0pt][c]{#2}};}}
\robustify{\circled}

\newcommand{\circling}[2][]{\tikz[baseline=(char.base)]
    {\node[shape = circle, draw = gray!100, inner sep = 1pt, fill= gray!100]
    (char) {\phantom{\ifblank{#1}{#2}{#1}}};%
    \node at (char.center) {\makebox[0pt][c]{#2}};}}
\robustify{\circled}


\begin{document}
%\setcopyright{acmcopyright}

\title{When Deep Learning Meets Captcha}
\author{
%\IEEEauthorblockN{Guixin Ye\IEEEauthorrefmark{2},
%Zhanyong Tang$^{*,}$\IEEEauthorrefmark{2}\thanks{*Corresponding authors: Zhanyong Tang and Zheng Wang},
%Dingyi Fang\IEEEauthorrefmark{2},
%Xiaojiang Chen\IEEEauthorrefmark{2},
%Kwang In Kim\IEEEauthorrefmark{3},
%Ben Taylor\IEEEauthorrefmark{4}, and
%Zheng Wang$^{*,}$\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}School of Information Science and Technology, Northwest University, China\\Email:  gxye@stumail.nwu.edu.cn, \{zytang, dyf, xjchen\}@nwu.edu.cn}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science, University of Bath, UK\\Email: k.kim@bath.ac.uk}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}School of Computing and Communications, Lancaster University, UK\\Email: \{b.d.taylor, z.wang\}@lancaster.ac.uk}
}

\IEEEoverridecommandlockouts
\makeatletter\def\@IEEEpubidpullup{9\baselineskip}\makeatother
\IEEEpubid{\parbox{\columnwidth}{Permission to freely reproduce all or part
    of this paper for noncommercial purposes is granted provided that
    copies bear this notice and the full citation on the first
    page. Reproduction for commercial purposes is strictly prohibited
    without the prior written consent of the Internet Society, the
    first-named author (for reproduction of an entire paper only), and
    the author's employer if the paper was prepared within the scope
    of employment.  \\
    NDSS '17, 26 February -1 March 2017, San Diego, CA, USA\\
    Copyright 2017 Internet Society, ISBN 1-891562-41-X\\
    http://dx.doi.org/10.14722/ndss.2017.23xxx
}
\hspace{\columnsep}\makebox[\columnwidth]{}}

\maketitle

\begin{abstract}

CAPTCHA is a standard secure mechanism to automated tell computers and humans, and is applied to prevent against malicious bot programs. Current text-based Captcha mechanism combines many anti-segmentation and anti-recognition features such as sophisticated noisy background, character rotation, distortion and overlapping. Such mechanism is widely deployed by Google, Microsoft, Baidu, Alibaba. Many attacks on text-based Captcha have been proposed. However, most of these fine prior works focus on a unique Captcha mechanism, making them have a limited applicability. In this paper, we demonstrate a novel generic attack on current text-based Captcha. We employ the Generative Adversarial Networks (GANs) to translate the original Captcha to the regular one. Using the translated regular Captcha to train a Convolutional Neural Network (CNN) model, our approach is able to accurately identify the Captcha. We thoroughly evaluated our approach using real-world Captchas, and achieve a success rate of over XX with an average speed of 76ms on an ordinary server (with a 3.2-GHz Inter Xeon CPU with 100-GB RAM and a TITAN Xp GPU). We discovered that, the Captcha with complex noisy background do not defend against segmentation under our attack. This is demonstrated by the fact that we are able to remove the complex background from the Captcha image. Since our attack can identify a widely text-based Captchas, this paper calls the community to revisit the risks of using text-based Captcha to defend against malicious bots.
\end{abstract}

\begin{IEEEkeywords}
    Captcha, Security, Generic Attack, Text-based
\end{IEEEkeywords}

%\begin{CCSXML}
%<ccs2012>
%<concept>
%<concept_id>10002978.10002991.10002992.10011618</concept_id>
%<concept_desc>Security and privacy~Graphical / visual passwords</concept_desc>
%<concept_significance>500</concept_significance>
%</concept>
%<concept>
%<concept_id>10002978.10003014.10003017</concept_id>
%<concept_desc>Security and privacy~Mobile and wireless security</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%</ccs2012>
%\end{CCSXML}
%
%\ccsdesc[500]{Security and privacy~Graphical / visual passwords}
%\ccsdesc[300]{Security and privacy~Mobile and wireless security}
%
%\printccsdesc
% no keywords
%\keywords{Captcha, Security, GAN, Text-based}\\

%TODO:
% Read: A pilot study on the security of pattern screen-lock methods and soft side channel attacks
\input{introduction}
\input{background}
\input{generator}
\input{overview}
\input{details}
\input{experimental_setup}
\input{results}
\input{related}
\input{conclusion}
%\input{materials}
%\input{related}

\section*{Acknowledgements}
    We would like to thank all participants who help for completing the experiments. Thank all volunteers for their time and insights as well as the anonymous reviewer for their critical and constructive comments. This work was supported by NSFC (Grant No. 61672427) and the UK Engineering and Physical Sciences Research Council (Grants No. EP/M01567X/1(SANDeRs) and EP/M015793/1(DIVIDEND)).

%\begin{spacing}{0.98}
\bibliographystyle{IEEEtranS}
\balance
\bibliography{refs}
%\end{spacing}

\end{document}
